\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeScholarshipHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Joey Shi} \\ \vspace{1pt}
    \small
    \href{https://joeyshi.xyz}{\raisebox{-0.1\height}\faUser\ \underline{joeyshi.xyz}} ~
    \href{mailto:root@joeyshi.xyz}{\raisebox{-0.2\height}\faEnvelope\  \underline{root@joeyshi.xyz}} ~
    \href{https://linkedin.com/in/joeyshi12/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/joeyshi12}}  ~
    \href{https://github.com/joeyshi12}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/joeyshi12}}
    \vspace{-8pt}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Scala \textperiodcentered{} Java \textperiodcentered{} TypeScript \textperiodcentered{} HTML \textperiodcentered{} CSS \textperiodcentered{} Python \textperiodcentered{} C/C++ \textperiodcentered{} Bash \textperiodcentered{} SQL \textperiodcentered{} Julia} \\
     \textbf{Frameworks/Libraries}{: Angular \textperiodcentered{} Jasmine \textperiodcentered{} Node.js \textperiodcentered{} D3.js \textperiodcentered{} Flask \textperiodcentered{} Pandas \textperiodcentered{} PyTest \textperiodcentered{} Javalin \textperiodcentered{} ScalaTest} \\
     \textbf{Tools/Technologies}{: Git \textperiodcentered{} Linux \textperiodcentered{} Docker \textperiodcentered{} Android Studio \textperiodcentered{} Vim} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{Jul 2020 -- Apr 2023}
      {Teaching Assistant}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Led tutorials for 2 different sections of a third-year computer networking course.}
        \resumeItem{Designed PrarieLearn exam questions for the computer networking course.}
        \resumeItem{Acommodated first-year calculus tutorials for 2 different sections.}
        \resumeItem{Implemented WeBWorK questions in Perl for calculus assignments and exams.}
    \resumeItemListEnd

    \resumeSubheading
      {Vital Mechanics Research}{May 2022 -- Oct 2022}
      {Software Developer}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Researched topics in geometry processing and CAD software for clothing simulation.}
        \resumeItem{Developed pipeline for extracting and inferring garment geometry and stitches from GLTF and DXF files.}
        \resumeItem{Applied numerical methods and graph theoretic approaches to infer information about garment stitching.}
    \resumeItemListEnd

    \resumeSubheading
      {Visier Inc.}{Jan 2021 -- Dec 2021}
      {Full-Stack Software Developer}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Built end-to-end features using tools, such as Scala and Angular.}
        \resumeItem{Co-led an epic with 2 other project members to deliver a feature for resolving tenant data issues within the application.}
        \resumeItem{Built a Scala backend API for reporting and correcting data issues in tenant data versions.}
        \resumeItem{Mentored other co-op students on REST APIs, network debugging, and traversing large code repositories.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Computer Review Site} $|$ \emph{Javalin \textperiodcentered{} JDBC \textperiodcentered{} SQL}}{Nov 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Collaborated in a group of 3 to design a full-stack web application for reviewing computers.}
            \resumeItem{Implemented backend database operations and SQL queries.}
            \resumeItem{Setup Maven configurations and build scripts.}
            \resumeItem{Dockerized and deployed application on a personal Raspberry Pi.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Multiplayer Browser Platformer} $|$ \emph{TypeScript \textperiodcentered{} Node \textperiodcentered{} Socket.IO \textperiodcentered{} Docker}}{Dec 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Designed a real-time multiplayer browser platformer using the HTML5 Canvas API.}
            \resumeItem{Built a backend web socket API to update and broadcast player data.}
            \resumeItem{Implemented logic for player movement, animation, physics, map design, and tile collision.}
            \resumeItem{Dockerized and deployed application on a personal Raspberry Pi.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Differential Equation Solver} $|$ \emph{Python \textperiodcentered{} Matplotlib \textperiodcentered{} Tkinter}}{Dec 2019 -- Present}
          \resumeItemListStart
            \resumeItem{Implemented efficient finite difference algorithms to solve ordinary and partial differential equations.}
            \resumeItem{Designed a graphical user interface in Tkinter and added animated plots for visualizing the generated solutions.}
            \resumeItem{Built a CI/CD pipeline with PyTest, Tox, and Github Actions.}
            \resumeItem{Published the application on the Python Package Index.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{Sep 2018 -- May 2023}
      {Bachelor of Science $|$ Combined Major in Computer Science and Math}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Cumulative GPA: 91\%}
        \resumeItem{Dean's Honour List (2018 -- 2021); Science Scholar (2019)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%---------SCHOLARSHIPS---------
\section{Scholarships}
  \resumeSubHeadingListStart
    \resumeScholarshipHeading
      {\textbf{Stanley M. Grant Scholarship in Mathematics}}{Jan 2021}
    \resumeScholarshipHeading
      {\textbf{Charles and Jane Banks Scholarship}}{Sep 2020}
    \resumeScholarshipHeading
      {\textbf{Trek Excellence Scholarship}}{Aug 2020}
  \resumeSubHeadingListEnd
\end{document}

